% \newgeometry{left=0.5in,right=0.5in,top=1in,bottom=1.4in}
\begin{acknowledgments}
    I have been incredibly fortunate and privileged throughout my life to have been given many opportunities that have led me to pursue this thesis research. Thanks to all of the people who have provided me with the environment, safety, health, financial well-being, love, joy, support, and knowledge to produce this work.

    First and foremost, I would like to thank my advisor, Deepak Pathak, for his guidance, support, and mentorship throughout my Masters.
    I am incredibly thankful for the unparalleled opportunities he has given me to grow as a researcher, and for taking an early bet on me.
    I would also like to thank my close collaborator, Alyosha Efros, for his mentorship and guidance throughout my Masters. It has been an incredible experience to learn from and work with him.
    I would also like to thank Deva Ramanan for taking the time to serve on my committee and providing early feedback on my work.

    % Alex Li (phd student of deepak's), co-author of our internet explorer project --- served as a mentor, collaborator, and great friend throughout my masters.
    Next, I would like to give a special thanks to Alex Li for his mentorship, guidance, collaboration, and friendship throughout my Masters. I could not have asked for a better collaborator on the Internet work---I hope that we have the opportunity to work together again in the future.

    Thanks to all of my other close friends at CMU in Smith Hall, NSH, and beyond for making my time here fly by. This includes
    Shivam Duggal,
    Ananye Agarwal,
    Mihir Prabhudesai,
    Haoyu Xiong,
    Xuxin Cheng,
    Zipeng Fu,
    David Noursi,
    Sacha Bartholme,
    Nilay Pande,
    Tanmay Kulkarni,
    Sudeep Dasari,
    Helen Jiang,
    Jason Zhang,
    Peter Manohar,
    Shikhar Bahl,
    Aditya Kannan,
    Alvin Shek,
    Aaron Trowbridge,
    and many others.

    Looking back, my teachers and mentors earlier in my life ignited my interests in computer science and mathematics and later opened my eyes to the world of research.
    In high school,
    I was fortunate to have wonderful mathematics teachers in
    Joan Llufrio and Amy Scheer, who taught me to love problem solving;
    at the same time, my water polo coach, Don Casey, taught me the importance of hard work, discipline, and delayed gratification.
    During undergrad at Vanderbilt,
    Gerald Roth and Graham Hemingway taught me to love computer science, and I will be forever grateful to Maithilee Kunda for taking a chance on me and introducing me to artificial intelligence and the world of research as a second semester senior.
    
    After Vanderbilt at BlackRock, I was fortunate to have the opportunity to work with an incredible cast of people at their AI Labs, who helped cement my desire to pursue graduate school. I am especially thankful to Rachel Schutt for selecting me as a founding member of the group, and for her mentorship and guidance throughout my time there. I am also thankful to my manager, Alex McKay, for his mentorship and guidance, and my close friends and colleagues, including
    Melanie Manko,
    Don Weidner,
    Mike Sereiko,
    Sri Bhupatiraju,
    Jeevan Acharya,
    Jason Motylinski,
    Shawn Simpson,
    Jack Gindi,
    Hristo Paskov,
    Nick Moehle,
    Steven Diamond,
    Shane Barrett,
    and others.
    I would also like to thank our senior advisors for their close guidance and support, including
    Mykel Kochenderfer,
    Stephen Boyd,
    Trevor Hastie,
    and Rob Tibshirani.

    I would be remiss not to mention the support I have received from the Native American community throughout my graduate school journey. From my first research presentation opportunity at AISES, the guidance on application procedures and personal mentorship, and financial support in the form of scholarships through AISES and the Osage Nation---it is safe to say that I would not be where I am today without this wonderful community.

    On the personal side, I would like to thank all of my other friends and family members that have provided me with an immense amount of love, support, and encouragement throughout the years---especially my girlfriend Mara, who has been by my side through it all.
    Thanks to my parents John and Amy;
    siblings Marnie and Evan;
    and the rest of my extended family
    for raising me in a wonderful environment and
    encouraging me at every step along the way.
\end{acknowledgments}
% \restoregeometry